Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex

@@

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened these differences in peak magnitudes through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yielding slightly better AUROC with $c=0.9 \in (0, 1)$.

After filter $c$, we applied a filter $w^*$ similar to $w$, whose goal is also
to magnify the importance of spikes that occur in case of low global activity.
Instead of equation \ref{eq:magnify-filter}, we had
\begin{align}
 w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
\end{align}
where the function $k$ is a piecewise linear function optimized for each filter
$f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
the reader to the implementation \footnote{available on
\url{https://github.com/asutera/kaggle- connectomics}.}.

\subsection*{Averaging the connectome inference from partial correlation statistics}

In our experiments, we observed that the inference process is quite sensitive
about the choice of the parameter value $\tau$ and the low-pass filter.
Therefore, in order to reduce the variance of the results and thus the
robustness of our approach, we perform an average over a range of parameter
value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
the four low-pass filters with the following parameters
\begin{align*}
weight_{f_1} &= 1,\\
weight_{f_2} &= 0.9, \\
weight_{f_3} &= 0.7, \\
weight_{f_4} &= 0.01
\end{align*}
tuned to maximize the ROC AUC on \textit{normal-1}.

>>>>

\textcolor{red}{Introduce each section as in the introduction of the article }

@@

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened these differences in peak magnitudes through
\begin{align}
p(x^t_i) = (x_i^t)^c
\end{align}
yielding slightly better AUROC with $c=0.9 \in (0, 1)$.

After filter $p$, we applied a filter $w^*$ similar to $w$, whose goal is also
to magnify the importance of spikes that occur in case of low global activity.
Instead of equation \ref{eq:magnify-filter}, we had
\begin{align}
 w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
\end{align}
where the function $k$ is a piecewise linear function optimized for each filter
$f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
the reader to the implementation \footnote{available on
\url{https://github.com/asutera/kaggle- connectomics}.}.

\subsection*{Weighted average of partial correlation statistics}

The AUROC performance of the conjunction of the composed function $w^* \circ p
\circ g \circ h \circ f_1$ (respectively $f_2$, $f_3$ and $f_4$) and the
partial correlation statistics was quite sensitive to the choice of $\tau$, the
hard threshold value and the design of the low pass filter. Similarly to the
simplified method, we average the partial correlation statistics obtained by
varying $\tau$ linearly from $0.100$ to $0.209$ and the low-pass filter.

Given the unequal AUROC performance of $f_1$, $f_2$, $f_3$ and $f_4$, the
contribution of each filter in the degree of association between two neurons
was chosen as to maximize the AUROC on \textit{normal-1} and is function of
their individual performance. By comparison in the simple method, each filter
$f_1$ and $f_2$ were given equal weight.

% In our experiments, we observed that the inference process is quite sensitive
% about the choice of the parameter value $\tau$ and the low-pass filter.
% Therefore, in order to reduce the variance of the results and thus the
% robustness of our approach, we perform an average over a range of parameter
% value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
% the four low-pass filters with the following parameters
% \begin{align*}
% weight_{f_1} &= 1,\\
% weight_{f_2} &= 0.9, \\
% weight_{f_3} &= 0.7, \\
% weight_{f_4} &= 0.01
% \end{align*}
% tuned to maximize the ROC AUC on \textit{normal-1}.
